%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Blue Acorn} % Organization
    {Senior Applications Engineer} % Job title
    {May 2014 - Feb 2017} % Dates
    {Charleston, SC} % Location
    {
      \begin{cvitems} % Description of tasks/responsibilities
        \item {Streamlined deployment pipeline across the organization.}
        \item {Pushed the most contributions to internal modules.}
        \item {Improved developer experience via Tampermonkey scripts and zsh plugins.}
        \item {Achieved the most "Play of the Sprint" awards in 2015.}
        \item {Promoted from Apprentice to Senior within two years for exemplary work quality and productivity.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {SIB Development \& Consulting}
    {Reporting Analyst}
    {Sep 2013 - May 2014}
    {Charleston, SC}
    {
      \begin{cvitems}
        \item {Contributed to unclogging the largest bottleneck in company operations, using Acrobat and Excel.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AstroParticule et Cosmologie}
    {Research Assistant}
    {Summer 2011}
    {Paris, France}
    {
      \begin{cvitems}
        \item {Conducted research and data analysis in correlation of temperature variation and phase noise for LOT (LISA On Table), an optical simulator for the LISA mission, under Dr. Hubert Halloin.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Valparaiso University}
    {Research Assistant}
    {Summer 2010}
    {Valparaiso, IN}
    {
      \begin{cvitems}
        \item {Explored pattern avoidance in ternary trees (combinatorial mathematics) in a team of three undergraduate students under mentor Dr. Lara Pudwell.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
