% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage[hidelinks]{hyperref}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Samuel Chong Tay}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{852 Centerwood Drive}
 \moveleft.5\hoffset\centerline{Charleston, SC 29412}
 \moveleft.5\hoffset\centerline{(631) 291-3866}

\begin{resume}

\section{TODO}
  Add more technical skills in computing skills \\

\section{EDUCATION}
  {\sl Bachelor of Arts} \hfill 2013 \\
  {\sl Kenyon College} \hfill Gambier, OH \\
  {\sl Major}: Mathematics; {\sl Concentration}: Scientific Computing \\
  {\sl GPA}: 3.91 \\
  {\sl Relevant Coursework:} Data Structures and Program Design, Parallel Computing, Computational Algebraic Coding Theory, Calculus, Linear Algebra, Mathematical Logic, Number Theory, Abstract Algebra, Real Analysis

\section{HONORS AND AWARDS}
  {\sl Phi Beta Kappa Society} \\
  {\sl Pi Mu Epsilon National Mathematics Honor Society} \\
  {\sl Newman's Own Scholarship}, Kenyon College \\
  {\sl Zakov Family Scholarship}, Kenyon College \\
  {\sl John H. Dunlap IV Scholarship}, Kenyon College.
    Funding for deserving mathematics majors who have demonstrated excellence in
    the programming and/or use of computer applications. \\
  {\sl Distinction on Senior Thesis}, Kenyon College, 2013 \\
  {\sl The Reginald B. Allen Prize}, Kenyon College, 2013.
    Annual award to a student who the professors of the Department of
    Mathematics decide has done the most outstanding work in mathematics. \\
  {\sl The Wendell D. Lindstrom Memorial Prize}, Kenyon College, 2011 \\
  {\sl Undergraduate Poster Session Award}, Joint Mathematics Meeting, 2011

\section{RESEARCH EXPERIENCE}
  {\sl Research Assistant} \hfill        Summer 2011 \\
  AstroParticule et Cosmologie \hfill Paris, France
  \begin{itemize}
    \item Conducted research investigating the correlation of temperature variation and
      phase noise for LOT (LISA On Table), an optical simulator for the LISA mission,
      under Dr. Hubert Halloin.
  \end{itemize}

  {\sl Research Assistant} \hfill        Summer 2010 \\
  Valparaiso University \hfill Valparaiso, IN
  \begin{itemize}
    \item Explored pattern avoidance in ternary trees (combinatorial mathematics) in a
      team of three undergraduate students under mentor Dr. Lara Pudwell.
  \end{itemize}

\section{TEACHING EXPERIENCE}
  {\sl Math Tutor} \hfill        Summer 2012 \\
  Independent Support Services \hfill Rock Hill, NY
  \begin{itemize}
    \item Tutored an autistic client in math and successfully increased placement exam
      scores, allowing the client to pursue their desired program at the SUNY Nassau
      Community College.
  \end{itemize}

  {\sl Lead Tutor} \hfill        January 2011 - May 2013 \\
  Kenyon College, Math and Science Skills Center \hfill Gambier, OH
  \begin{itemize}
    \item Attend class and assist with teaching Calculus and Maple syntax.
  \end{itemize}

\section{WORK EXPERIENCE}
  {\sl Software Engineer} \hfill August 2017 - Present \\
  Wrinkl, Inc. \hfill Charleston, SC
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Full stack development of a websocket-driven chat application in Haskell.
    \item Leverage advanced type system features to achieve a high level of code safety.
    \item Languages: Haskell, Nix.
  \end{itemize}

  {\sl Applications Engineer} \hfill May 2014 - February 2017 \\
  Blue Acorn \hfill Charleston, SC
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Developed reusable modules in an object oriented MVC eCommerce framework.
    \item Contributed to internal infastructure in the form of deployment tools,
      Hipchat addons, and a docker composition-machine management tool.
    \item Languages: PHP, Javascript, Bash.
  \end{itemize}

\section{COMPUTER \\ SKILLS}
  {\sl Languages}: Fluent in Haskell, Javascript, PHP, Python, C++. Experience with Bash, C. \\
  {\sl Operating Systems}: Linux and Mac OS.

\section{PUBLICATIONS}
  {\sl Pattern Avoidance in Ternary Trees} \\
  Nathan Gabriel, Katherine Peske, Lara Pudwell, and Samuel Tay \\
  Journal of Integer Sequences 15 (2012) 12.1.5. \\
  \url{http://arxiv.org/abs/1110.2225}

\end{resume}
\end{document}
