% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Samuel Chong Tay}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{852 Centerwood Drive}
 \moveleft.5\hoffset\centerline{Charleston, SC 29412}
 \moveleft.5\hoffset\centerline{(631) 291-3866}

\begin{resume}
 
% TODO Update this objective
\section{OBJECTIVE}
  A dynamic position in software development that allows learning
  and expanding into new technologies to solve interesting problems.
  % TODO make this less boilerplate

\section{EDUCATION}
  {\sl Bachelor of Science}, 2013 \\
  Kenyon College, Gambier, OH \\
  Major: Mathematics \\
  Minor: Scientific Computing \\
  GPA: 3.91 \\
  Honors: % TODO Current resume pdf is missing full honors & awards
 
 
\section{COMPUTER \\ SKILLS}
  {\sl Languages \& Software:} Fluent in Javascript, C++, and PHP.
    Experience in bash scripting and writing docker compositions. \\ 
  {\sl Operating Systems:} Linux and Mac OS.
 
\section{EXPERIENCE}
  {\sl Senior Applications Engineer} \hfill May 2014 - Present \\
  Blue Acorn, Charleston, SC
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Extensive Magento development experience both in transforming particular
      client requirements into custom features and in building abstract reusable modules
      for use on any client site.
    \item Contributed to internal infastructure initiatives such as deployment tools, 
      Hipchat Connect addons, and a docker composition-machine management tool.
    \item Promoted from Apprentice to Applications Engineer II to Senior Applications Engineer
      within two years
  \end{itemize}

  {\sl Reporting Analyst} \hfill            September 2013 - May 2014 \\
  SIB Development and Consulting
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Built reports using Excel and Acrobat to validate savings for clients.
  \end{itemize} 

  {\sl Math Tutor} \hfill        Summer 2012 \\
  Independent Support Services, Rock Hill, NY
  \begin{itemize}
    \item Tutored an autistic client in math and successfully increased placement exam
      scores, allowing the client to pursue their desired program at the SUNY Nassau
      Community College.
  \end{itemize} 
 
  {\sl Research Assistant} \hfill        Summer 2011 \\
  AstroParticule et Cosmologie, Paris, France
  \begin{itemize}
    \item Conducted research and data analysis in correlation of temperature variation and
      phase noise for LOT (LISA On Table), an optical simulator for the LISA mission,
      under Dr. Hubert Halloin.
  \end{itemize} 

  {\sl Research Assistant} \hfill        Summer 2010 \\
  Valparaiso University, Valparaiso, IN
  \begin{itemize}
    \item Explored pattern avoidance in ternary trees (combinatorial mathematics) in a
      team of three undergraduate students under mentor Dr. Lara Pudwell.
  \end{itemize} 

\section{PUBLICATIONS}             
  “Pattern Avoidance in Ternary Trees”, Nathan Gabriel, Katherine Peske,
  Lara Pudwell, and Samuel Tay, Journal of Integer Sequences 15 (2012) 12.1.5. \\
  \url{http://arxiv.org/abs/1110.2225}

\end{resume}
\end{document}
