%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \longdatecventry
    {Software Engineer}
    {SimSpace}
    {Dec 2018 - Sep 2019, Jun 2020 - Present}
    {Remote}
    {
      \begin{cvitems}
        \item {\color{graytext}\textbf{APIs}}: Develop APIs for various services
          that comprise a realistic network simulation product for cybersecurity
          training.
        \item {\color{graytext}\textbf{Languages}}: Haskell, SQL.
        \item {\color{graytext}\textbf{Technologies}}: AWS, Docker, Kubernetes,
          Minio, Postgres, Servant.
      \end{cvitems}
    }

  \cventry
    {Teaching Assistant}
    {University of Washington}
    {Sep 2019 - Jun 2020}
    {Seattle, WA}
    {
      \begin{cvitems}
      \item {\color{graytext}\textbf{Teaching}}: Wrote lesson plans and led recitation classes
        for undergraduate probability and statistics courses.
      \item {\color{graytext}\textbf{Learning}}: Took graduate classes such as Statistical Inference, Network
        Optimization, Graphical Models,\\ Machine Learning, Programming Language
        Theory.
        \item {\color{graytext}\textbf{Languages}}: Python, R, Coq.
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Full Stack Developer}
    {Wrinkl}
    {Aug 2017 - Sep 2019}
    {Remote}
    {
      \begin{cvitems}
        \item {\color{graytext}\textbf{App Development}}: Developed a
          websocket-driven chat application, supporting
          web, iOS, and Android apps.
        \item {\color{graytext}\textbf{FRP}}: Used the Reflex FRP library to
          develop highly dynamic user interfaces with declarative strongly-typed
          code.
        \item {\color{graytext}\textbf{Languages}}: Haskell, SQL, Nix.
        \item {\color{graytext}\textbf{Technologies}}: Hydra, NixOS, Postgres,
          Reflex-Platform, Snap.
      \end{cvitems}
    }

%---------------------------------------------------------
  %\cventry
    %{Software Developer}
    %{ExpandShare}
    %{Apr 2017 - Aug 2017}
    %{Charleston, SC}
    %{
      %\begin{cvitems}
        %\item {Built core features and microservices for a Learning Manage System.}
        %\item {Languages: Python, Javascript.}
      %\end{cvitems}
    %}

%---------------------------------------------------------
  \cventry
    {Applications Engineer} % Job title
    {Blue Acorn} % Organization
    {May 2014 - Feb 2017} % Dates
    {Charleston, SC} % Location
    {
      \begin{cvitems} % Description of tasks/responsibilities
        \item {\color{graytext}\textbf{Magento}}: Developed reusable modules in
          an object oriented MVC eCommerce framework.
        \item {\color{graytext}\textbf{Developer Initiatives}}: Founded an
          educational Functional Programming group with weekly meetups.
        \item {\color{graytext}\textbf{Lead Developer}}: Led an agile team
          and mentored junior developers.
        \item {\color{graytext}\textbf{Languages}}: PHP, Javascript, Bash.
        \item {\color{graytext}\textbf{Technologies}}: Ansible, KnockoutJS, Magento,
          MySQL, RabbitMQ, Zend.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
