%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=2.4cm, top=.8cm, right=2.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-emerald}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
\name{Samuel Chong}{Tay}
\position{Software Engineer{\enskip\cdotp\enskip}Mathematician}
\address{852 Centerwood Drive, Charleston, SC 29412}
\email{sam.chong.tay@gmail.com}
\mobile{(631) 291-3866}
\homepage{samtay.github.io}
\github{samtay}
\linkedin{sam-tay}
\reddit{algebra4life}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Recruitment Team}
  {COMPANY\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Résumé}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Samuel Chong Tay~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
As a graduate of a rigorous axiomatic mathematics curriculum, I have an
  appreciation for the abstract and the ability to pay meticulous attention to
  detail while maintaining a larger perspective.  These skills have been
  invaluable as I've built the foundation of my career as a software developer.
  My previous employer, Blue Acorn, hired me as an apprentice with no
  development experience; since those humble beginnings I have mastered the
  Magento framework in PHP, engineered a robust RabbitMQ integration framework,
  built a chat-opts deployment tool in Node, written countless Bash and Zsh
  scripts, created a docker composition orchestration tool in Haskell, and
  founded a collaborative functional programming education group.  Most
  recently, at ExpandShare, I jumped into a custom Django and
  AngularJS app and started contributing from day one.

\lettersection{Why COMPANY?}
As a mathematics and functional programming enthusiast, I am particularly
  excited by this position and I believe I can offer a fresh, valuable
  perspective to the dev team.  I've been in a Haskell deep dive since I first
  discovered the language and have already completed a number of projects, such
  as \underline{\href{https://github.com/samtay/tetris}{Tetris}},
  \underline{\href{https://github.com/samtay/conway}{Life}}, and
  \underline{\href{https://github.com/samtay/dockmaster}{Dockmaster}}.
  I've scratched the surface with Elm and love its obviously-Haskell-inspired
  paradigms, and I really enjoyed listening to Evan Czaplicki talk about his
  inspiration for the language and his opinions on what a compiler should be.
  I've also heard great things about Elixir and am intrigued by the Erlang
  ecosystem in general. I relish the opportunity to broaden my skill set with
  these elegant technologies alongside such talented teammates.

\lettersection{Why Me?}
In addition to development skills, I feel I would excel at COMPANY due to my
  impressive work ethic and team mentality.  I do not settle for mediocrity and
  I firmly believe in the importance of sharing knowledge and accepting
  constructive criticism.  Most importantly, I am very motivated to learn more
  and am committed to the functional paradigm.  If you have any questions about
  this letter or my resume, please do not hesitate to contact me.  Thank you
  for taking the time to consider my application.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
