% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Samuel Chong Tay}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{852 Centerwood Drive}
 \moveleft.5\hoffset\centerline{Charleston, SC 29412}
 \moveleft.5\hoffset\centerline{(631) 291-3866}

\begin{resume}
 
\section{OBJECTIVE}
  A dynamic position in software development that allows learning
  and expanding into new technologies to solve interesting problems.
  % TODO make this less boilerplate

\section{EDUCATION}
  {\sl Bachelor of Science} \hfill 2013 \\
  Kenyon College \hfill Gambier, OH \\
  Major: Mathematics; Minor: Scientific Computing \\
  GPA: 3.91
\section{COMPUTER \\ SKILLS}
  {\sl Languages \& Software:} Fluent in PHP, Javascript, and C++.
    Experience in bash scripting and writing docker compositions. \\
  {\sl Operating Systems:} Linux and Mac OS.
 
\section{EXPERIENCE}
  {\sl Senior Applications Engineer} \hfill May 2014 - Present \\
  Blue Acorn \hfill Charleston, SC
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Transformed client requirements into custom features and built abstract reusable modules.
    \item Contributed to internal infastructure initiatives such as deployment tools,
      Hipchat Connect addons, and a docker composition-machine management tool.
    \item Promoted from Apprentice to Senior Applications Engineer within two years.
  \end{itemize}

  {\sl Reporting Analyst} \hfill            September 2013 - May 2014 \\
  SIB Development and Consulting \hfill Charleston, SC
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Built reports using Excel and Acrobat to validate savings for clients.
  \end{itemize}

  {\sl Math Tutor} \hfill        Summer 2012 \\
  Independent Support Services \hfill Rock Hill, NY
  \begin{itemize}
    \item Tutored an autistic client in math and successfully increased placement exam
      scores, allowing the client to pursue their desired program at the SUNY Nassau
      Community College.
  \end{itemize} 
 
  {\sl Research Assistant} \hfill        Summer 2011 \\
  AstroParticule et Cosmologie \hfill Paris, France
  \begin{itemize}
    \item Conducted research and data analysis in correlation of temperature variation and
      phase noise for LOT (LISA On Table), an optical simulator for the LISA mission,
      under Dr. Hubert Halloin.
  \end{itemize} 

  {\sl Research Assistant} \hfill        Summer 2010 \\
  Valparaiso University \hfill Valparaiso, IN
  \begin{itemize}
    \item Explored pattern avoidance in ternary trees (combinatorial mathematics) in a
      team of three undergraduate students under mentor Dr. Lara Pudwell.
  \end{itemize} 

\section{PUBLICATIONS}             
  {\sl Pattern Avoidance in Ternary Trees} \\
  Nathan Gabriel, Katherine Peske, Lara Pudwell, and Samuel Tay \\
  Journal of Integer Sequences 15 (2012) 12.1.5. \\
  \url{http://arxiv.org/abs/1110.2225}

\end{resume}
\end{document}
