%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Senior Software Engineer}
    {Sunscreen}
    {Oct 2022 - Present}
    {Remote}
    {
      \begin{cvitems}
        \item {\color{graytext}\textbf{Open Source}}: Maintained our open source
          \href{https://github.com/Sunscreen-tech/Sunscreen}{FHE compiler} and
          wrote user documentation, tutorials, and integrations.
        %\item {\color{graytext}\textbf{Mentor}}: Mentored an intern through a
          %greenfield project to make a debugger for our FHE and ZKP compilers.
        \item {\color{graytext}\textbf{Languages}}: Rust.
      \end{cvitems}
    }

  \cventry
    {Senior Software Engineer}
    {Phylum}
    {Apr 2022 - Oct 2022}
    {Remote}
    {
      \begin{cvitems}
        \item {\color{graytext}\textbf{APIs}}: Developed APIs internal and
          external parties to interact with our supply chain security package
          scoring data.
        \item {\color{graytext}\textbf{Data}}: Maintained an interface between the
          OLAP and OLTP areas of our product.
        \item {\color{graytext}\textbf{Languages}}: Rust, Scala, SQL.
        %\item {\color{graytext}\textbf{Technologies}}:
          %AWS, Docker, HBase, Kubernetes, Postgres, Redis, Spark.
      \end{cvitems}
    }


  \longdatecventry
    {Software Engineer}
    {SimSpace}
    {Dec 2018 - Apr 2022}
    {Remote}
    {
      \begin{cvitems}
        \item {\color{graytext}\textbf{APIs}}: Developed APIs for various services
          that comprise a realistic network simulation product for cybersecurity
          training.
        \item {\color{graytext}\textbf{Postgres}}: Regularly alleviated
          performance problems by analyzing and improving Postgres query plans.
        \item {\color{graytext}\textbf{Languages}}: Haskell, SQL.
        %\item {\color{graytext}\textbf{Technologies}}: AWS, Docker, Kubernetes,
          %Minio, Postgres, Servant.
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Full Stack Engineer}
    {Wrinkl}
    {Aug 2017 - Nov 2018}
    {Remote}
    {
      \begin{cvitems}
        \item {\color{graytext}\textbf{App Development}}: Developed a
          websocket-driven chat application, supporting
          web, iOS, and Android apps.
        \item {\color{graytext}\textbf{FRP}}: Used the Reflex FRP library to
          develop highly dynamic user interfaces with declarative strongly-typed
          code.
        \item {\color{graytext}\textbf{Languages}}: Haskell, SQL, Nix.
        %\item {\color{graytext}\textbf{Technologies}}: Hydra, NixOS, Postgres,
          %Reflex-Platform, Snap.
      \end{cvitems}
    }

%---------------------------------------------------------
  %\cventry
    %{Software Developer}
    %{ExpandShare}
    %{Apr 2017 - Aug 2017}
    %{Charleston, SC}
    %{
      %\begin{cvitems}
        %\item {Built core features and microservices for a Learning Manage System.}
        %\item {Languages: Python, Javascript.}
      %\end{cvitems}
    %}

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Blue Acorn} % Organization
    {May 2014 - Feb 2017} % Dates
    {Charleston, SC} % Location
    {
      \begin{cvitems} % Description of tasks/responsibilities
        \item {\color{graytext}\textbf{Magento}}: Developed and maintained
          eCommerce sites and reusable modules on the Magento platform.
        %\item {\color{graytext}\textbf{Lead}}: Led an agile team
          %and mentored junior developers.
        \item {\color{graytext}\textbf{Initiative}}: Founded an
          educational Functional Programming group with weekly meetups.
        \item {\color{graytext}\textbf{Languages}}: PHP, Javascript, Bash.
        %\item {\color{graytext}\textbf{Technologies}}: Ansible, KnockoutJS, Magento,
          %MySQL, RabbitMQ, Zend.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
